### 2011-02-10 paper/learningMethods.tex
spelling
NM shrink

\subsection{Parametrized Gaits}
\seclabel{motionModel}

@@

\subsection{Learning Methods for Parametrized Gaits}
\seclabel{learningMethods}

@@

\item \emph{Nelder-Mead simplex method}: The Nelder-Mead simplex
  method \cite{nm} creates an initial simplex with $d+1$ vertices,
  where $d$ is the dimension of the parameter space. The initial
  parameter vector is stored as the first vertex and the other five
  vertices are created by adding to one dimension at a time one tenth
  of the allowable range for that parameter. It then tests the fitness
  of each vertex, and, in general, it reflects the worst point over
  the centroid in an attempt to improve it.  However, to prevent
  cycles and becoming stuck in local minima, several other rules are
  used.  If the reflected point is better than the second worst point
  and worse than the best point, then the reflected point replaces the
  worst. If the reflected point is better than the best point, the
  simplex is expanded in the direction of the reflected point. The
  better of the reflected and the expanded point replaces the worst
  point. If the reflected point is worse than the second worst point,
  then the simplex is contracted away from the reflected point. If the
  contracted point is better than the reflected point, the contracted
  point replaces the worst point. If the contracted point is worse
  than the reflected point, the entire simplex is shrunk \cite{nm}.

>>>>

\subsection{Parameterized Gaits}
\seclabel{motionModel}

@@

\subsection{Learning Methods for Parameterized Gaits}
\seclabel{learningMethods}

@@

%\item \emph{Nelder-Mead simplex method}: The Nelder-Mead simplex
%  method \cite{nm} creates an initial simplex with $d+1$ vertices,
%  where $d$ is the dimension of the parameter space. The initial
%  parameter vector is stored as the first vertex and the other five
%  vertices are created by adding to one dimension at a time one tenth
%  of the allowable range for that parameter. It then tests the fitness
%  of each vertex, and, in general, it reflects the worst point over
%  the centroid in an attempt to improve it.  However, to prevent
%  cycles and becoming stuck in local minima, several other rules are
%  used.  If the reflected point is better than the second worst point
%  and worse than the best point, then the reflected point replaces the
%  worst. If the reflected point is better than the best point, the
%  simplex is expanded in the direction of the reflected point. The
%  better of the reflected and the expanded point replaces the worst
%  point. If the reflected point is worse than the second worst point,
%  then the simplex is contracted away from the reflected point. If the
%  contracted point is better than the reflected point, the contracted
%  point replaces the worst point. If the contracted point is worse
%  than the reflected point, the entire simplex is shrunk \cite{nm}.

\item \emph{Nelder-Mead simplex method}: The Nelder-Mead simplex
  method \cite{nm} creates an initial simplex with $d+1$ vertices,
  where $d$ is the dimension of the parameter space. It then tests the
  fitness of each vertex, and, in general, it reflects the worst point
  over the centroid in an attempt to improve it.  Several additional
  rules are used to prevent cycles and local minima \cite{nm}.
